---
title: "Alcohol vs Seat choice"
author: "Omar Challan"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
From what the graph shows, we are able to say that the box for students sitting in the back of the class is much bigger than those who seat in the front and middle, leading to the understanding that the students who sit in the back are more likely to pick up alcohol.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


The numerical data shows that the average number of drinks for the people seated in the back is about 9 drinks.
This is three times the average number of drinks for those who are seated in the middle. 
This is also nine times average number of drinks for those who are seated in the front.


## Inferential Tests

## Conclusions


